\huge Microbial Interaction Database pipeline - Figures draft \#2

### 2018-12-19 figures.tex
Update figure3

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure3.pdf}
  \caption{
    \textbf{Comparison of taxonomy assignments using different taxonomy reference databases}
    \textbf{(A)} Taxonomy composition of the 20 most abundant genera predicted using different taxonomy references databases: Greengenes, SILVA and NCBI.
    The legend shows the common and the unique genera among the taxonomy assignments.
    \textbf{(B)}
  }
  \label{fig:figure3}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure3.pdf}
  \caption{
    \textbf{Comparison of taxonomy assignments using different taxonomy reference databases}
    \textbf{(A)} Taxonomy composition of the 20 most abundant genera predicted using different taxonomy references databases: Greengenes, SILVA and NCBI.
    The legend shows the common and the unique genera among the taxonomy assignments.
    \textbf{(B)} The percentage of OTUs assigned to the same taxonomic label when using different reference databases.
    The percentage of matches are shown at various taxonomic levels.
    \textbf{(C)} The bray-curtis dissimilarity between the original taxonomy profile and calculated taxonomy profile in the mock datasets.
  }
  \label{fig:figure3}
\end{figure}
